Universal Anonymous Signatures

### 2022-09-20 prism-backend/research/gsac/formal-uas.tex
Rolled-back to 2 separate unforgeability properties.

% In addition, we define two auxiliary properties for defining
% the expected behaviour of the \ExtractIssue and \ExtractSign functions.
% \todo{The following may need to be moved elsewhere and/or re-written.}
% For instance, the extraction type are used in
% \cite{lnpy21,nps22}, and functions of the identify type are used in
% \cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
% these techniques when there is no traditional notion of opening. Since, mostly
% the unforgeability and non-frameability properties build on the extractability
% and identifiability ones, we define them first. Then, we proceed with the usual
% notions.

% \todo{Maybe do some drawing of the cred tree.}

% In the following, we use some custom notation to refer to the tree-like
% relationships that may be built between credentials and, more concretely, their
% related data (like {\usk}s, {\cid}s, and attribute sets {\attrs}s) when a user
% leverages previously obtained credentials in order to obtain new ones. To
% facilitate the explanation, we refer to \figref{fig:cred-tree}. In a nutshell,
% we use $tree_{\cid}$ to refer to the whole tree of {\cid}s that have been used
% to produce the credential with identifier \cid -- and, similarly, $tree_{\usk}$
% for {\usk}s, and $tree_{\attrs}$ for attribute sets.

% \begin{figure}[htp!]
%   \centering
%   \includegraphics[width=0.5\textwidth]{figures/cred-tree.png}
%   \caption{Credential trees, and their corresponding notation.
%     We use $Tree_x$, where $x \in \lbrace \usk,\cid,\attrs \rbrace$ to
%     denote the whole tree of {\usk}s, {\cid}s, and {\attrs}s. \\
%     \todo{Move to Tikz.}}
%   \label{fig:cred-tree}
% \end{figure}

% \paragraph{Extractability.} %
% We require that the witnesses used to produce each credential and signature can
% be extracted from the corresponding \utrans and signature, respectively.
% Furthermore, in order for our generalized notion of utility to be sound, it
% is required that, whenever a credential is issued by an honest issuer, \fissue
% accepts the extracted witnesses; and whenever a signature is accepted by
% \Verify, the extracted witnesses match the expected outputs by \feval and
% \finsp. We capture this in the \ExpExtractIssue and \ExpExtractSign games, which
% are crucial in the unforgeability and non-frameability requirements.

% In the extractability variant for credentials, \ExpExtractIssue, the adversary
% wins if it manages to get a credential produced by an honest issuer, such that
% the issuance predicate \fissue rejects the extracted witnesses, or if some of
% the involved credentials is associated to a different \usk.
% %
% In the variant for signatures, \ExpExtractSign, the adversary wins if the
% witnesses extracted from a signature accepted by \Verify make \feval and \finsp
% output inconsistent values.
% %
% The oracles available in \ExpExtractIssue is, $\OExt \gets (\lbrace\HU,\CU
% \rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$. Note that,
% for \ExpExtractIssue, honest issuers are required, as we rely on the
% availability of $\langle \Obtain,\Issue \rangle$ transcripts to assist on the
% extraction. On the other hand, for \ExpExtractSign, as we extract directly from
% signatures, honest issuers are not a requirement, so the adversary is given
% access to $\ICORR$ too.

% \begin{figure*}[htp!]
%   \centering
%   \scalebox{0.85}{
%     \begin{minipage}[t]{0.6\textwidth}
%       \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\OExt}(\parm) \\
%         (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \gets
%         \ExtractIssue(\trap,\trans[\cid]) \\
%         \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
%         \trans[\cid_i]) \\
%         \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
%         \pcif \fissue(\usk,\ATTR[\cid],\lbrace \cid_i \rbrace_{i \in [n]},
%         \lbrace\attrs_i\rbrace_{i \in [n]}) = 0: \\
%         \pcind \pcreturn 1 \\
%         \pcreturn 0
%       }
%     \end{minipage}
%     \vspace*{0.5em}

%     \begin{minipage}[t]{0.5\textwidth}
%       \procedure[linenumbering]{$\ExpExtractSign(1^\secpar)$}{%
%         (\parm, \trap) \gets \SimSetup(1^\secpar) \\
% 	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
%         \adv^{\OExt,\ICORR}(\parm) \\
% 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
% 	(\usk,\lbrace (\cid_i,\attrs_{\cid_i},\cdot) \rbrace_{i\in[n]},
%         \yeval^1,\yinsp) \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
%         (\yeval^0,\yeval^1) \gets \feval(\usk,\lbrace\cid_i\rbrace_{i \in [n]},
%         \lbrace\attrs_i\rbrace_{i \in [n]}, \msg) \\
%         \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
%         \pcreturn 1 \\
%         \pcif \finsp((\yeval^0,\yeval^1),\usk,\lbrace\cid_i\rbrace_{i \in [n]},
%         \lbrace\attrs_i\rbrace_{i \in [n]},\msg) \neq \yinsp:
%         \pcreturn 1 \\
% 	\pcreturn 0
%       }
%     \end{minipage}
%   }
%   \caption{Extractability experiments for \UAS schemes.}
%   \label{fig:exp-uas-extract}
% \end{figure*}

% \paragraph{Identifiability.} %
% On their own, the extractability properties only ensure that credentials and
% signatures have been produced by leveraging knowledge of some witnesses.
% However, they do not establish any relationship between those witnesses and
% users. While the actual technicalities of doing so is dependent on the
% construction, we can, modelling-wise, enforce constraints that associate
% user identifiers ({\uid}s, tracked by the game environment) with potential
% witnesses. Namely, we require that it must be possible to associate any
% credential (obtained from an honest issuer), or any signature accepted by
% \Verify, with exactly one user identifier.

% As for extractability, we define two variants. For credentials, in
% \ExpIdentifyCred we require the adversary to output the identifier of a
% credential obtained from an honest issuer. The adversary wins if, given the
% witnesses extracted from the corresponding transcript, the \IdentifyCred helper
% function outputs a set \suid of user identifiers with cardinality different than
% $1$.
% %
% Similarly, for signatures, the adversary wins if it is able to produce a
% signature from which the extracted witnesses, when passed to \IdentifySig,
% output a set \suid of user identifiers with cardinality different than $1$.
% %
% The oracles are as in the extractability experiments. Namely, in the
% \ExpIdentifyCred game, the adversary has access to $\OId \gets (\lbrace\HU,\CU
% \rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$, while in
% \ExpIdentifySign it also has access to \ICORR. The same reasoning applies.

% \begin{figure*}[htp!]
%   \centering
%   \scalebox{0.85}{
%     \begin{minipage}[t]{0.6\textwidth}
%       \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\OId}(\parm) \\
%         (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
%         \pcfor \cred \in \scred: \\
%         \pcind \suid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
%         \pcind \pcif |\suid| \neq 1: \pcreturn 1 \\
%         \pcind \pcif \suid~\textrm{differs from previous iterations}: \\
%         \pcind \pcind \pcreturn 1 \\
%         \pcreturn 0
%       }
%     \end{minipage}
%     \vspace*{0.5em}

%     \begin{minipage}[t]{0.5\textwidth}
%       \procedure[linenumbering]{$\ExpIdentifySign(1^\secpar)$}{%
%         (\parm, \trap) \gets \SimSetup(1^\secpar) \\
% 	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\OId,\ICORR}(\parm) \\
% 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
% 	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets
%         \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
% 	\suid \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
% 	\pcif |\suid| \neq 1: \pcreturn 1 \\
% 	\pcreturn 0
%       }
%     \end{minipage}
%   }
%   \caption{Identifiability experiments for \UAS schemes.}
%   \label{fig:exp-uas-identify}
% \end{figure*}

% \begin{definition}{(Identifiable credentials in \UAS)}
%   \label{def:identify-cred-uas}  
%   We define the advantage \AdvIdCred of $\adv$ against \ExpIdentifyCred as
%   $\AdvIdCred=|\Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack-
%   \Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack|$.
%   %
%   An \UAS scheme \emph{with extractable issuance} satisfies identifiable
%   credentials if, for any p.p.t. adversary $\adv$, \AdvIdCred is a negligible
%   function of $1^\secpar$.
% \end{definition}

% \begin{definition}{(Identifiable signatures in \UAS)}
%   \label{def:identify-sig-uas}  
%   We define the advantage \AdvIdSign of $\adv$ against \ExpIdentifySign as
%   $\AdvIdSign=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
%   \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
%   %
%   An \UAS scheme \emph{with extractable signatures} satisfies identifiable
%   signature if, for any p.p.t. adversary $\adv$, \AdvIdSign is a negligible
%   function of $1^\secpar$.
% \end{definition}

@@

\paragraph{Unforgeability.} \UAS inherits from AC schemes the notion that no
adversary can prove claims unless it owns credentials with the proper
attributes -- although, in \UAS, claims can be proven at issuance time, and
at signing time; from GS schemes, it inherits that only credential owners can
produce valid signatures. \UAS also has verifiable openings, and we must ensure
that the values output by \Open are correct and trace back to a user with
consistent credentials. All the previous is captured by an unforgeability
property. We define it by allowing the adversary to call any oracle, except the
one for corrupting issuers. The adversary wins if it produces a valid signature
that:  (1) the produced signature leveraged a credential for
which the conditions required by \fissue were not satisfied; (2), opens to a
wrong value, or to a value that cannot be processed by \Judge; (3), is not
consistent with the expected \Yeval value; or (4), cannot be associated to
known credentials owned by a known user.
%
Note that, under this definition, we do not consider a forgery a credential that
was issued without meeting the issuance policy unless it is used to produce
a signature accepted by \Verify. Indeed, obtaining credentials that cannot be
used later does not seem to pose a threat in the real world. This approach,
which greatly simplifies the modelling, has also been used before (e.g.
\cite{ckl+15}).
%
\ExpForge is formally defined in \figref{fig:exp-uas-unfor}).

\begin{figure}[htp!]
  \centering
  \scalebox{0.85}{
    \begin{minipage}[t]{\textwidth}
%       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
%         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
%         \cid \gets \adv^{\Oforgeissue}(\parm) \\
%         \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
%         \pcreturn 0 \\
%         \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
%         \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
%         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
%         ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
%         \gets \ExtractIssue(\trap,\utrans) \\
%         % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
%         % \trans[\cid_i]) \\
%         % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
%         \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
%         \rbrace_{i\in[n]}) \neq \yissue:
%         \pcreturn 1 \\
%         \pcif \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup \CU:
%         \pcreturn 1 \\
% %        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
% %        \uid \in \HU \cup \CU: \pcreturn 1 \\
% %        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
%         \pcreturn 0
%       }
%       \vspace*{0.5em}

    % \end{minipage}    
    % \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]: \pcreturn 0 \\
        \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
        \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
        \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
        = 0: \pcreturn 1 \\
        % (\usk,\sCred,\tyeval^1,\yinsp') \gets
        % \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        % \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
        % \pcreturn 0
	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
        \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        \pcif \exists i\in[n]~\suchthat~
        \fissue(\upk,\cid_i,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
        \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
        \OWNR[\cid_i \cup \lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
        \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
        (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
        \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans): \\
        \pcind \pcreturn 1 \\        
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg)
        \neq \yinsp \lor \yinsp \neq \yinsp':
        \pcreturn 1 \\
%        \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
        \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
        \pcreturn 1 \\        
        \pcreturn 0        
      }      
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
  \label{fig:exp-uas-unfor}
\end{figure}

% \begin{figure}[htp!]
%     \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
%       (\parm,\trap) \gets \Setup(1^\secpar) \\
%       (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
%       \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
%       \SIG[\uid]: \pcreturn 0 \\
%       \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
%       \pcreturn 0 \\
%       (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
%       \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
%       = 0: \pcreturn 1 \\
%       (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
%       \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
%       % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
%       % \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
%       % \pcreturn 1 \\
%       % \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
%       % \pcreturn 1 \\
%       \uid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
%       \uid' \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
%       \pcif \uid \neq \uid' \lor \uid \notin \HU \cup \CU: \pcreturn 1 \\
%       %\pcif \exists \cred \in \scred~\suchthat~
% %      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
%       % \pcreturn 1 \\
%       % \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
%       % \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
%       \pcreturn 0
%     }
%   \caption{Experiment for unforgeability of signatures in \UAS schemes.}
%   \label{fig:exp-uas-unfor-sign}
% \end{figure}

% \begin{definition}{(Unforgeable issuance of \UAS)}
%   \label{def:issue-forge-uas}  
%   We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
%   $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
%   \AdvForgeIssue is a negligible function of $1^\secpar$.
% \end{definition}

% \begin{definition}{(Unforgeable signing of \UAS)}
%   \label{def:sign-forge-uas}  
%   We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
%   $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
%   \AdvForgeSign is a negligible function of $1^\secpar$.
% \end{definition}

@@

\begin{definition}{(Unforgeability of \UAS)}
  \label{def:forge-uas}  
  We define advantage \AdvForge of $\adv$ against \ExpForge as $\AdvForge=
  \Pr\lbrack\ExpForge(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme is unforgeable if, for any p.p.t. adversary $\adv$, \AdvForge is
  a negligible function of $1^\secpar$.
\end{definition}

>>>>

@@

\paragraph{Unforgeability.} In \UAS schemes, we need to prevent forging either
credential requests, or signatures. The latter is mostly a combination of the
unforgeability of AC schemes, and the traceability of GS schemes with verifiable
openings. However, issuance unforgeability is a direct consequence of allowing
proving arbitrary claims already when requesting credentials.

In more detail, issuance unforgeability captures that all the credentials issued
by an honest issuer meet the requirements set by the corresponding issuance
function. Moreover, any credential used to support the request needs to belong
to a known user. Without conventional opening, we need to resort to extraction.
The adversary is required to output a credential identifier that must correspond
to an existing credential issuance interaction -- note that the transcript must
be available to us if it exists, as the issuer is honest. From this transcript,
we extract the witness used to compute the issuance function, which includes the
output of the issuance function claimed by the requestor, and the credential
identifiers of any used credential. The adversary wins if applying the output of
the issuance function applied to the extracted witness is not consistent, or if
the credential identifiers do not belong all to the same (known) user.

Signature unforgeability is simply a combination of known requirements in AC and
GS schemes. Namely, the adversary is required to output a valid signature, and
wins if the signature: (1) opens to a wrong value, or to a value that cannot be
processed by \Judge; (2), is not consistent with the expected $\Yeval =
(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to known credentials
owned by a known user.

The respective properties, \ExpForgeIssue and \ExpForgeSign, are formally
defined in \figref{fig:exp-uas-unfor}).

% \begin{figure}[htp!]
%   \centering
%   \scalebox{0.85}{
%     \begin{minipage}[t]{\textwidth}
%       \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
%         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
%         (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
%         \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
%         \SIG[\uid]: \pcreturn 0 \\
%         \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
%         \pcreturn 0 \\
%         (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
%         \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
%         = 0: \pcreturn 1 \\
% 	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
%         \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
%         \pcif \exists i\in[n]~\suchthat~
%         \fissue(\upk,\cid_i,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
%         \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
%         \OWNR[\cid_i \cup \lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
%         \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
%         (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
%         \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans): \\
%         \pcind \pcreturn 1 \\        
%         (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
%         \rbrace_{i\in[n]}, \msg) \\
%         \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
%         \pcreturn 1 \\
%         \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
%         \rbrace_{i\in[n]},\msg)
%         \neq \yinsp \lor \yinsp \neq \yinsp':
%         \pcreturn 1 \\
%         \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
%         \pcreturn 1 \\        
%         \pcreturn 0        
%       }      
%     \end{minipage}
%   }
%   \caption{Unforgeability experiments in \UAS schemes.
%     $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
%     \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
%   \label{fig:exp-uas-unfor}
% \end{figure}

\begin{figure}[htp!]
  \centering
  \hspace*{-2em}
  \scalebox{0.85}{
    \begin{minipage}[t]{0.6\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforge}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
        \pcreturn 0 \\
        (\yissue,\utrans) \gets \trans[\cid];
        ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\        
        (\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
        \pcind \gets \ExtractIssue(\trap,\utrans) \\
        \pcreturn \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup
        \CU~\lor \\
        \pcind \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) \neq \yissue        
      }      
    \end{minipage}    
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]~\lor  \\
        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
        \pcind \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
	(\upk,\cdot,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
        \tyeval^1,\tyinsp) % \pcskipln
        \\
        \pcind \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
        \HU \cup \CU~\lor \\
        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
        \msg,\feval) = 0~\lor \\
        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
        \yinsp \neq \tyinsp~\lor\\
        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg) \neq \yinsp 
      }
    \end{minipage}
  }
  \caption{Unforgeability experiments in \UAS schemes.
    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
  \label{fig:exp-uas-unfor}
\end{figure}

\begin{definition}{(Unforgeable issuance of \UAS)}
  \label{def:issue-forge-uas}  
  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
  \AdvForgeIssue is a negligible function of $1^\secpar$.
\end{definition}

\begin{definition}{(Unforgeable signing of \UAS)}
  \label{def:sign-forge-uas}  
  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
  %
  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
  \AdvForgeSign is a negligible function of $1^\secpar$.
\end{definition}

@@

% \begin{definition}{(Unforgeability of \UAS)}
%   \label{def:forge-uas}  
%   We define advantage \AdvForge of $\adv$ against \ExpForge as $\AdvForge=
%   \Pr\lbrack\ExpForge(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme is unforgeable if, for any p.p.t. adversary $\adv$, \AdvForge is
%   a negligible function of $1^\secpar$.
% \end{definition}
